---
title: "HW2_arflowers"
author: "Anna Flowers"
date: "9/8/2021"
output: pdf_document
---

# Homework 2

## Problem 2

### Part A

### Part B

## Problem 3

## Problem 4

``` {r}
#install.packages('data.table')
library(data.table)
covid_raw <- fread("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
us <- covid_raw[covid_raw$countriesAndTerritories == 'United_States_of_America',]
us_filtered <- us[us$month %in% c(6:7),]
us_filtered$index <- rev(1:dim(us_filtered)[1]) 
fit<-lm(`Cumulative_number_for_14_days_of_COVID-19_cases_per_100000`~index, data=us_filtered)
```

### Part A

#### 1

```{r}
library(knitr)
kable(summary(us_filtered))
```

#### 2

```{r}
library(stargazer)
stargazer(fit)
```

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & `Cumulative\_number\_for\_14\_days\_of\_COVID-19\_cases\_per\_100000` \\ 
\hline \\[-1.8ex] 
 index & 4.107$^{***}$ \\ 
  & (0.145) \\ 
  & \\ 
 Constant & 42.853$^{***}$ \\ 
  & (5.165) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 61 \\ 
R$^{2}$ & 0.932 \\ 
Adjusted R$^{2}$ & 0.930 \\ 
Residual Std. Error & 19.922 (df = 59) \\ 
F Statistic & 803.464$^{***}$ (df = 1; 59) \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### Part B

```{r}
#install.packages("broom")
fit.diags <- broom::augment(fit)
```

### Part C

## Problem 5

## Problem 6